---
title       : Iris Species Identification
subtitle    : Shiny Application
author      : Hong Fan
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
github:
  user: rainbowfan
  repo: DataProductsDeveloping/ShinyApp/slidifyDemo
---

## Iris Dataset in R

1.Description

This data set contains 150 iris flowers' measurements in centimeters of sepal length, sepal width, petal length and petal width. 150 flowers belong to 3 species. They are iris setosa, iris versicolor and iris virginica. 

2.Summary of Each Variable

```{r echo=F, results='asis', message=FALSE}
summary(iris)
```

---

## Figure 1 Sepal Length vs Sepal Width
```{r, warning=FALSE, message=FALSE, echo=F}
library(plotly)
M1 = plot_ly(iris, type="scatter", x = ~Sepal.Length, y = ~Sepal.Width, mode = "markers", color = ~Species)
htmlwidgets::saveWidget(M1, file = "demo1.html")
```
<iframe src="demo1.html" style="position:absolute;height:80%;width:90%"></iframe>

---

## Figure 2 Petal Length vs Petal Width
```{r, warning=FALSE, message=FALSE, echo=F}
library(plotly)
M2 = plot_ly(iris, type="scatter", x = ~Petal.Length, y = ~Petal.Width, mode = "markers", color = ~Species)
htmlwidgets::saveWidget(M2, file = "demo2.html")
```
<iframe src="demo2.html" style="position:absolute;height:80%;width:90%"></iframe>

---

## K Nearest Neighbors in Iris Identification Shiny App

1. Sepal length, sepal width, petal length and petal width are the characteristics used to predict unknown iris species. 

2. Euclidean distance is calculated to compare the closeness. 

3. Users have the flexibility to choose the parameter k which is the number of neighbors used to predict the unknown iris species. 








